%========================================
% 11 | Uddissanagāthā
%========================================
\section*{e11 | Uddissanagāthā}

\begin{chantsubsection}
  \chantnote
    {\{Handa mayaṃ uddissanagāthāyo bhaṇāmase\}}
  \chantnotetrans
    {\{Now let us recite the verses of dedication.\}}
\end{chantsubsection}

\begin{chantsubsection}
  \chantlinepair
    {Iminā puññakammena}
    {Upajjhāyā guṇuttarā}
    {By this meritorious deed, may my preceptors of superior virtue [benefit].}

  \chantlinepair
    {Ācariyūpakārā ca}
    {Mātā pitā ca ñātakā piyā mamaṃ}
    {May my teachers and benefactors, my mother and father, and my dear relatives [benefit].}

  \chantlinepair
    {Suriyo candimā rājā}
    {Guṇavantā narāpi ca}
    {The sun, the moon, kings, and virtuous people as well,}

  \chantlinepair
    {Brahmamārā ca indā ca}
    {Lokapālā ca devatā}
    {the Brahmās, Māras, Indas, guardian deities, and gods,}

  \chantlinepair
    {Yamo mittā manussā ca}
    {Majjhattā verikāpi ca}
    {Yama, friends, human beings, the impartial, and even enemies,}

  \chantlinepair
    {Sabbe sattā sukhī hontu}
    {Puññāni pakatāni me}
    {may all beings be happy through the merits I have made.}

  \chantlinepair
    {Sukhaṃ ca tividhaṃ dentu}
    {Khippaṃ pāpetha vomataṃ}
    {May they bestow the threefold happiness and quickly reach Nibbāna.}

  \chantlinepair
    {Iminā puññakammena}
    {Iminā uddisena ca}
    {By this meritorious deed and by this dedication,}

  \chantlinepair
    {Khippāhaṃ sulabhe ceva}
    {Taṇhupādānachedanaṃ}
    {may I swiftly and easily attain the cutting off of craving and clinging.}

  \chantlinepair
    {Ye santāne hinā dhammā}
    {Yāva nibbānato mamaṃ}
    {Whatever inferior states exist in my mental continuum until Nibbāna,}

  \chantlinepair
    {Nassantu sabbadā yeva}
    {Yattha jāto bhave bhave}
    {may they always disappear, wherever I am reborn, life after life.}

  \chantlinepair
    {Ujucittaṃ satipaññā}
    {Sallekho vīriyamhinā}
    {May I have a straight mind, mindfulness and wisdom, and purification through effacement and energy.}

  \chantlinepair
    {Mārā labhantu nokāsaṃ}
    {Kātuñca vīriyesu me}
    {May Māra find no opportunity to obstruct my efforts.}

  \chantlinepair
    {Buddho dīpavaro nātho}
    {Dhammo nātho varuttamo}
    {The Buddha, the excellent lamp, is my refuge; the Dhamma is my supreme refuge.}

  \chantlinepair
    {Nātho paccekabuddho ca}
    {Saṅgho nāthottaro mamaṃ}
    {The Paccekabuddha is my refuge, and the Saṅgha is my highest refuge.}

  \chantlinepair
    {Tesottamānubhāvena}
    {Mārokāsaṃ labhantu mā}
    {By the power of these supreme ones, may Māra gain no opportunity [over me].}
\end{chantsubsection}
