\section*{Homage to the Great Master Phramongkolthepmuni}

\begin{chantsubsection}

\chantlinepair
{Gom grahb ma nat nohm}
{wa ra jom wi chaa jarn}
{With reverent devotion, we bow in homage to the Great Master.}

\chantlinepair
{Nop ong pra song yaan}
{chi na boot chi noh dome}
{We honor the noble one, a true heir to the Victor's (Jina's) way.}

\chantlinepair
{Aek song pra naam jan-}
{ta-sa-roh wi sut som}
{Supreme and singular, pure and radiant in virtue.}

\chantlinepair
{Tuay tep ma nut prom}
{a pi wan ta naa gaan}
{Honored and revered by devas, humans, and Brahmās.}

\chantlinepair
{Taan wang wi mut ponh}
{chana gohn pa yaa marn}
{He opened the way to liberation, triumphing over the Lord of Māra.}

\chantlinepair
{Mung sut na ruh paan}
{a ti yaan pra nam chai}
{He strives toward Nibbāna, guided by noble wisdom.}

\chantlinepair
{Plea sheep ta wai saat}
{mu ni naat na pen sai}
{He upheld the true discipline, the Sage beyond reproach.}

\chantlinepair
{Yoot ning sa nit nai}
{ha ruh tai na glang gai}
{Steadfast and composed, firm in heart and mind.}

\chantlinepair
{Duang tam sa waang lam}
{pah hu tammagai prai}
{The light of Dhamma shines forth, illuminating every path.}

\chantlinepair
{Hen sut da lort saai}
{wa ra gai wi set saan}
{With sublime insight, he sees clearly through all realms.}

\chantlinepair
{witcha pra chaan chiaow}
{ma na diaow pa jone marn}
{Master of profound knowledge, single-minded against defilements.}

\chantlinepair
{Braab sin gi laet raan}
{a pi barn ma ha chon}
{He uprooted unwholesome states, bringing benefit to the multitude.}

\chantlinepair
{Ruu jaeng gra jang jin}
{pra ta win ja ruam pohn}
{Clearly knowing cause and effect, he unites wisdom with fruition.}

\chantlinepair
{Yoot ningh lu makh pohn}
{a nu sohn pra toan tan}
{Abiding firmly in attainment, worthy of constant recollection.}

\chantlinepair
{Yom dai mi yom pae}
{ma na nae mi prae pan}
{Never defeated, never shaken by delusion.}

\chantlinepair
{Gram suek tuk kern wan}
{sa la plun u tit plea}
{Waging the daily battle, he gave himself for the good of all.}

\chantlinepair
{Jai taan mi wan wai}
{ja ka yai pra saat sri}
{With unwavering heart, he upheld the noble dispensation.}

\chantlinepair
{Saang pra lae kon dee}
{ku na mee ta lort chon}
{He nurtured noble ones and good people with boundless compassion.}

\chantlinepair
{Duay dae cha sanh sern}
{su ja rern pi pat pohn}
{May his virtues bring growth, prosperity, and success.}

\chantlinepair
{Koh pohn pra mong kohn}
{taep mu nee pi chit marn}
{Through the blessing of Phramongkolthepmuni, conqueror of Māra.}

\chantlinepair
{Uai chai ma lai sohk}
{ni ra roak lu pai parn}
{May hearts be filled with joy, free from illness and danger.}

\chantlinepair
{Soab suk ga sem sarn}
{ta na jak kra paht mee}
{May happiness and well-being prevail throughout the land.}

\chantlinepair
{Ruu jaeng pra taam maa}
{lu wi cha pra chin na see}
{May insight into Dhamma and true knowledge arise.}

\chantlinepair
{Biam boon ya baa ra mee}
{suk ka san ni ran gaan}
{May merit and perfection flourish, bringing lasting peace.}

\end{chantsubsection}
