%========================================
% Section：[11] Pattidānagāthā
%========================================
\section*{m11 | Pattidāna-gāthā}

\begin{chantsubsection}
    \chantnote
    {\{Handa mayaṃ pattidāna gāthāyo bhaṇāma se\}}
    \chantnotetrans{\{Now let us recite the verses for sharing merit.\}}
\chantgap
  \chantline
    {Yā devatā santi vihāravāsinī, }
    {May the devas who dwell in this monastery,}
  \chantline
    {thūpe ghare bodhighare tahiṃ tahiṃ, }
    {in the stupa, the buildings, and the Bodhi-tree enclosure, here and there,}
  \chantline
    {tā dhammadānena bhavantu pūjitā, }
    {be honoured through this gift of Dhamma,}
  \chantline
    {sotthiṃ karontedha vihāramaṇḍale, }
    {and bring safety and well-being to this monastery compound.}

  \chantline
    {therā ca majjhā navakā ca bhikkhavo, }
    {May elder, intermediate, and newly ordained monks,}
  \chantline
    {sārāmikā dānapatī upāsakā, }
    {temple attendants, donors, and lay followers,}
  \chantline
    {gāmā ca desā nigamā ca issarā, }
    {villages, districts, towns, and their rulers,}
  \chantline
    {sappāṇabhūtā sukhitā bhavantu te, }
    {and all beings endowed with life, be happy.}

  \chantline
    {jalābujā yepi ca aṇḍasambhavā, }
    {Those born from the womb and those who come from an egg,}
  \chantline
    {saṃsedajātā athavopapātikā, }
    {those born from moisture, or who arise spontaneously,}
  \chantline
    {niyyānikaṃ dhammavaraṃ paṭicca te, }
    {having relied on the excellent Dhamma that leads out of suffering,}
  \chantline
    {sabbepi dukkhassa karontu saṅkhayaṃ, }
    {may they all bring about the ending of suffering.}

%% 下面开始 chantpair，节省空间
  \chantlinepair
    {thātu ciraṃ sataṃ dhammo, }
    {dhammaddharā ca puggalā, }
    {May the Dhamma of the good endure for a long time, together with the individuals who uphold the Dhamma.}

  \chantlinepair
    {saṅgho hotu samaggo va, }
    {atthāya ca hitāya ca, }
    {May the Sangha remain harmonious, for welfare and for benefit.}

  \chantlinepair
    {amhe rakkhatu saddhammo, }
    {sabbepi dhammacārino, }
    {May the true Dhamma protect us and all who practise in accordance with the Dhamma.}

  \chantlinepair
    {vuḍḍhiṃ sampāpuṇeyyāma, }
    {dhamme ariyappavedite. }
    {May we attain growth and fulfilment in the Dhamma taught and proclaimed by the Noble Ones.}

\end{chantsubsection}
