% Vince proofread

% title-en: Mettā Chanting (Spreading Loving Kindness)
\section*{m13 | Mettā Chanting (Spreading Loving Kindness)}\label{sec:m13}

\begin{chantsubsection}
  % Sabbe sattā – 总说一切众生
  \chantlineinline
    {Sabbe sattā}
    {All beings | All beings are our companions, born, growing old, falling ill, and dying together.}
  \chantindent
    {Sat-tang-lai, tee-ben-puen-tuk, gert-gae-jep-die, duay-gan mot-tang-sin.}
  \chantgap

  % Averā – 无瞋
  \chantlineinline
    {averā}
    {free from enmity | May we truly be happy and never use violence against one another.}
  \chantindent
    {Jong-ben-suk ben-suk-terd. Ya-dai-mee-wehn gae-gan-lae-gan-leuy.}
  \chantgap

  % Abyāpajjhā – 不互害
  \chantlineinline
    {abyāpajjhā}
    {free from ill will | May we truly be happy and never injure or oppress each other.}
  \chantindent
    {Jong-ben-suk-ben-suk-terd, ya-dai-biat-bian-seung-gan lae-gan-leuy.}
  \chantgap

  % Anīghā – 无苦恼
  \chantlineinline
    {anīghā}
    {free from affliction | May we truly be happy and have no suffering of body or mind at all.}
  \chantindent
    {Jong-ben-suk-ben-suk-terd, ya-dai-mee-kwam-tuk-gai-tuk-jai-leuy.}
  \chantgap

  % Sukhī attānaṃ pariharantu – 乐而自护
  \chantlineinline
    {sukhī attānaṃ pariharantu}
    {May they dwell in happiness | May you have happiness of body and mind, protecting yourselves from all suffering; may those who suffer find happiness, and may those who are happy grow even happier.}
  \chantindent
    {Jong-mee-kwam-suk-gai suk-jai, rak-sa-ton-hai-pon jak-tuk-pai, tang-sin-terd.}
  \chantindent
    {Tan-tang-lai, tee-tan dai-tuk, kor-hai-tan mee-kwam-suk, tan-tang-lai, tee-tan-dai-suk, kor-hai-suk-ying-ying-keurn-bai.}
  \chantgap

  % Sabbe sattā – 四生众生皆受功德
  \chantlineinline
    {sabbe sattā}
    {all beings | All beings who are egg-born, womb-born, moisture-born, or spontaneously born: may they receive this wholesome merit and blessing, each and every one.}
  \chantindent
    {Sat-tang-lai, tee-gerd-pen aṇ-ḍa-ja, tee-gerd-pen ja-lā-bu-ja, tee-gerd-pen saṃ-se-da-ja, tee-gerd-pen o-pa-pāti-ka, jong-ma-rap-gu-son-pohn boon, hai-tuan-tua tuk-tua-tuern.}
\end{chantsubsection}

